Compositional equivalences based on Open pNets

### 2020-02-28 2016-Weak-FH-Bisim/WeakBisim.tex
version eric 28/02
Draft 2eme exemple en page 26

>>>>

  \bigskip
  Now consider the $3^{rd}$ triple from the table, and transition $WI_{8'}(n)$ from state $100$ to state $000$ for some fixed integer $n$. It should correspond to $WS_7(n)$ of $b1$.

  $ WI_{8'}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s1-msg,s1-ec+n)}\}, True, ()}
         {100 \OTWeakarrow {\underline{\texttt{out(s1-msg,s1-ec+n)}}} 000}
         \ \forall n\ge 0$

  $ WS_7(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(msg,ec+n)}\subst{ec\gets ec+n}\}, True, (ec\gets ec+n)}
         {b1 \OTWeakarrow {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}} b0}
         \ \forall n\ge
         $

  \medskip       A similar reasonning gives us:

         $\{b1_msg = s1_msg \land b1_ec = s1_ec \land True\hspace{3mm} \implies
\\
(\texttt{q-recv(s1-msg,s1-ec+n)} = \texttt{q-recv(msg,ec+n)}
\land True\\
\land \underline{\texttt{out(s1-msg,s1-ec+n)}} = {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}}\\
\land True \subst{ec\gets ec+n})\}
$
